### 2014-11-13 tex/evaluation.tex
Fixed some typos with the evaluation.

In most tests, run times strongly favor \symtxt{}, especially for nontrivial k-values. Performance improvement ranges from 4.8x for BinarySearchTree at $k$=3, to 118x for LinkedList at $k$=6. In fact, a number of test cases can be efficiently completed using \symtxt{} for k-bounds that are not practical to be attempted with \gsetxt{} or lazier\#, including the BinarySearchTree for $k$=4 and LinkedList for $k$=8. Some of this discrepancy may be accounted for by the fact that \symtxt{} is equipped for incremental solving, however, during informal testing with the incremental solver turned off, \symtxt{} usually performed better than \gsetxt and lazier\#, especially in test runs with high k-bounds.

>>>>

In most tests, run times strongly favor \symtxt{}, especially for nontrivial k-values. Performance improvement ranges from 4.8x for BinarySearchTree at $k$=3, to 118x for LinkedList at $k$=6. In fact, a number of test cases can be efficiently completed using \symtxt{} for k-bounds that are not practical to be attempted with \gsetxt{} or lazier\#, including the BinarySearchTree for $k$=4 and LinkedList for $k$=8. Some of this discrepancy may be accounted for by the fact that \symtxt{} is equipped for incremental solving, however, during informal testing with the incremental solver turned off, \symtxt{} usually performed better than \gsetxt{} and lazier\#, especially in test runs with high k-bounds.
